The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2013-10-06 article.tex
Added two missing sections

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Availability and requirements}

\item \textbf{Project Name}: The Chemistry Development Kit
\textbf{Project home page}: \url{http://cdk.sourceforge.net/}
\textbf{Operating system(s)}: Windows, GNU/Linux, OS/X
\textbf{Programming language}: Java
\textbf{Other (optional) requirements}: JNI-InChI, Vecmath, BEAM, Guava, JGraphT, Signatures, CMLDOM, XOM, JavaCC
\textbf{License}: LGPL v2.1 or later
\textbf{Any restrictions to use by non-academics}: None additional
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Competing interests}
XX and YY have companies that sell solutions based on the CDK.
